Poster Data Analysis

### 2018-09-09 notebooks/poster_analysis.Rmd
added statistical test for comparison of qnr-genes

```{r, include = FALSE}
# Libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr, ggplot2, tidyr, cowplot, viridis, forcats, radiant.data)

@@

## Acquired genes per animal species
```{r}
gene_names <- names(resfinder_results)

@@

@@

>>>>

```{r, include = FALSE}
# Libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr, ggplot2, tidyr, cowplot, viridis, forcats, radiant.data, purrr)

@@

## Acquired genes per animal species
### Total acquired genes per animal species
```{r}
gene_names <- names(resfinder_results)

@@

### Qnr-genes per animal species
```{r}
qnr_genes <- c("qnrA1","qnrB19","qnrB6","qnrB60","qnrS1","qnrS2","qnrS4")

qnr_data <- resfinder_results %>%
  left_join(isolate_data, by = "id") %>%
  gather(key, value, qnr_genes) %>%
  group_by(key, value, species) %>%
  count() %>%
  ungroup() %>%
  mutate(value = if_else(value == 1, "Present", "Absent")) %>%
  spread(value, n, fill = 0) %>%
  rowwise() %>%
  mutate(Total = Present + Absent,
         Percent = round(Present/Total*100, 1),
         lwr = round(get_binCI(Present, Total)[1], 1),
         upr = round(get_binCI(Present, Total)[2], 1))

ggplot(qnr_data, aes(key, Percent, fill = species))+
  geom_col(color = "black",
           position = position_dodge(0.9))+
  geom_errorbar(aes(ymin = lwr, ymax = upr),
                width = 0.6,
                position = position_dodge(0.9))+
  scale_fill_brewer(palette = "Paired")+
  labs(y = "Percent (%) of isolates",
       fill = NULL)+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90, size = 8, hjust = 1, vjust = 0.4),
        axis.title.x = element_blank())
```

@@

# Statistics

## Significance test for the percent presence of qnrB19 and qnrS1 between animal species
```{r message=FALSE, warning=FALSE}
specific_qnr <- qnr_data %>%
  filter(key %in% c("qnrB19", "qnrS1")) %>%
  select(key, species, Present, Absent) %>%
  split(f = .$key)

do_chisq_test <- function(df) {
  df <- df %>%
    slice(expand.grid(1:length(unique(species)), 1:length(unique(species))) %>% rev %>% 
          filter(Var2 < Var1) %>% t) %>%
    mutate(test = rep(1:(n()/2), each = 2)) %>%
    group_by(test) %>%
    do(data_frame(gene = .$key,
                  test = first(.$test),
                  species1 = first(.$species),
                  species2 = last(.$species),
                  data = list(matrix(c(.$Absent,
                                       .$Present),
                                     ncol = 2)))) %>%
    mutate(chi_test = map(data, chisq.test, correct = FALSE)) %>%
    mutate(p.value = map_dbl(chi_test, "p.value"),
           dupl = duplicated(test)) %>%
    filter(dupl == FALSE) %>%
    select(gene, species1, species2, p.value) %>%
    filter(p.value < 0.05)
  return(df)
}

p_values <- lapply(specific_qnr, function(x) do_chisq_test(x)) %>%
  bind_rows(.id = "gene")

p_values
```
